FISTA with adaptive discretisations

### 2021-01-07 paper.tex
Rename aFEM_paper.tex to paper.tex
Update paper to remove page-break
Update text and figures
Mainly minor text/figure editing. I added more necessary details to the introduction/notation section and simplified the 1D convergence plots in the results.

\documentclass[10pt,a4paper,onecolumn]{article} \usepackage[latin1]{inputenc}
\usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm}
\usepackage[cm]{fullpage}
\definecolor{linkColor}{rgb}{0.5, 0.5, 0.5}
\usepackage[colorlinks, allcolors=linkColor, bookmarks=True]{hyperref}
\usepackage[capitalise]{cleveref}
\usetikzlibrary{positioning,trees}
\usepackage{algorithm,algpseudocode}
\graphicspath{{Figures/}}
\DeclareGraphicsExtensions{.pdf,.png}
\numberwithin{equation}{section}
\newtheorem{definition}{Definition}[section]\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\makeatletter\let\c@definition\c@theorem\let\c@definition\c@theorem\makeatother
\makeatletter\let\c@lemma\c@theorem\let\c@lemma\c@theorem\makeatother
\makeatletter\let\c@example\c@theorem\let\c@example\c@theorem\makeatother
\makeatletter\let\c@remark\c@theorem\let\c@remark\c@theorem\makeatother
\newtheorem*{theorem*}{Theorem}

\newcommand{\Partial}[2]{\frac{\partial #1}{\partial #2}}
\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\C{A}}
\newcommand{\Vector}[3]{ \begin{pmatrix} #1 \\ #2 \\ #3 \end{pmatrix}}
\newcommand{\MTwo}[4]{\begin{pmatrix} #1 & #2 \\ #3 & #4 \end{pmatrix}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}\newcommand{\overtext}[2]{\stackrel{\text{#1}}{#2}}
\newcommand{\xmapsfrom}[1]{\reflectbox{$\xmapsto{\reflectbox{\scalebox{0.87}[0.69]{$#1$}}}$}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\renewcommand{\P}{\F{P}}\newcommand{\E}{\F{E}}\newcommand{\1}{\F{1}}
\newcommand{\tab}{\indent}\newcommand{\Tab}{\newline\tab}
\renewcommand{\circle}[1]{\raisebox{.5pt}{\rm{\textcircled{\raisebox{-.9pt} {#1}}}}}
\newcommand{\intbar}{-\hspace{-10.5pt}\int}\newcommand{\todo}[1]{{\color{red}#1}}
\DeclareMathOperator{\st}{\;s.t.\;}\DeclareMathOperator{\as}{\;a.s.\;}\renewcommand{\epsilon}{\varepsilon}
\DeclareMathOperator*{\Union}{\bigcup}\DeclareMathOperator{\union}{\cup}
\DeclareMathOperator*{\Intersect}{\bigcap}\DeclareMathOperator{\intersect}{\cap}
\renewcommand{\bar}{\overline}\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\renewcommand{\vec}{\mathbf}
\DeclareMathOperator*{\argmin}{argmin}\DeclareMathOperator{\TV}{TV}
\DeclareMathOperator{\prox}{prox}\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}\DeclareMathOperator{\sign}{sign}

\newcounter{adaptStepCounter}
\newenvironment{adaptiveStep}{\refstepcounter{adaptStepCounter}}{}
\crefname{adaptStepCounter}{step}{steps}

@@

\author{Robert Tovey}
\date{\longdate\today}
\title{FISTA with adaptive discretisations}
\begin{document}
	\maketitle

%In many variational approaches to inverse problems, optimisation problems are often written in a continuous setting but solved with a discrete optimisation algorithm. Consider what happens when $\sqrt{e^2}$ is computed in your favourite programming language. We have asked a `continuous' question and have been given a `discrete' answer with very well controlled error bounds.
%
%The parallel to this for optimisation is that we still do not have infinite computing memory or processing power, but we still want to compute minimisers to a known accuracy with efficient implementations. It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \cite{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \cite{Mallat1999,Candes2004,Guo2007}. These are typically quite weak guarantees valid for asymptotic resolution/time and are hard to quantify in a specific example. In this work we propose an algorithm with three aims:
%\begin{itemize}
%	\item All computations are discrete but the asymptotic reconstruction is exact, even for infinite dimensional reconstructions in a Banach space, with a guaranteed rate.
%	\item Distance to the infinite dimensional minimiser can be quantified.
%	\item Discretisation is adaptively optimised for the particular minimiser.
%\end{itemize}
%
%We choose to modify the FISTA algorithm because it is quite general and performs very well in discrete optimisation problems. The strategy will be to follow the standard FISTA algorithm as closely as possible. The only difference is that at each iteration, computations will only be performed on a finite dimensional subspace. 
%
%One key issue is that FISTA is intrinsically designed to converge only in $L^2$. In finite dimensions there is no issue, all norms are equal and so convergence rates are equal for all problems up to scaling constants. On the other hand, in infinite dimensions there exist minimisers which are not in $L^2$. In this case, we find that the rate will always be slower than for standard FISTA but still at a guaranteed rate.
%
%We perform two numerical experiments where the minimiser is in $L^1\setminus L^2$ which demonstrates the reduced rate. We also show an example where the minimiser is in $\ell^2(\R^m)$ for some $m$ which is not known a priori and observe that the refining FISTA algorithm achieves linear convergence.

\section{Introduction}
The standard setting of the Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) is that there exists a Hilbert space $\F H$ over which we wish to minimise the function 
\begin{equation}\label{eq:ca: min F = fD+fC}
	\min_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
\end{equation}
where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function. FISTA is a practically fast algorithm which, for many choices of $\Func0$, generates a sequence of iterates $\varf0_n\in\F H$ such that $\Func0(\varf0_n)$ converges at the optimal rate of $O(n^{-2})$ \cite{Beck2009,Chambolle2015}.

The canonical example for this work will be the Lasso energy,
$$\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1$$
where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\R^d)\to \R^m$ is the forward map and $\mu>0$ is a chosen scalar. It is known that there exist minimisers of $\Func0$ of the form:
$$\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, $$
for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$ \cite{Unser2016,Boyer2019}. The challenge with this minimiser is that $\varf0^*\in L^1\setminus L^2$, so exact FISTA cannot be applied to this problem. On the other hand, $\varf0^*$ has a very nice structure which we expect can be easily and efficiently represented by, for instance, a basis of finite elements.

In this work we propose a modification of FISTA which addresses both of these points. During each iteration we restrict computation to a subspace, i.e. $\varf0_n\in\spcf0^n\subset\F H$.
For infinite dimensional optimisation, this allows us to reconstruct $\varf0^*$ to an arbitrary precision in finite time. Alternatively, for finite dimensional optimisation this potentially allows for a more computationally efficient variant of the classical FISTA algorithm.

Inexact optimisation is a well-established field which can be seen to encompass methods such as coordinate descent \cite{Wright2015}, stochastic gradient \cite{Spall2005,Bottou2018}, or indeed approximate FISTA-like algorithms \cite{Jiang2012,Villa2013}. The result of \Cref{thm:ca: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}. The key novelty is the concept of convergence outside of the Hilbert space $\F H$. Additionally assuming that errors come from quantified subspace approximations, we can also provide explicit rates.

\subsection{Outline}
This chapter is organised as follows. \Cref{sec:ca: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg:ca: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of \Cref{alg:ca: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec:ca: recipe}, then we state the specific results in the case of FISTA in \Cref{sec:ca: FISTA convergence}. The main results are \Cref{thm:ca: exponential FISTA convergence} and \Cref{thm:ca: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

\Cref{sec:ca: general examples} presents some general results for the application of \Cref{alg:ca: refining FISTA} and \Cref{sec:ca: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate $\varf0^*$, estimate the convergence of $\Func0$, and identify the support of $\varf0^*$. The numerical results in \Cref{sec:ca: numerics} demonstrate these techniques in four different models demonstrating the sharpness of our analysis and the computational efficiency of adaptive discretisations.

\section{Definitions and notation}\label{sec:ca: prelims}
We consider optimisation of \eqref{eq:ca: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
$$ \exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).$$
We further define
$$\Func0_0\colon \varf0\mapsto \Func0(\varf0)-\Func0(\varf0^*).$$
Note that $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be.

We propose a refining FISTA algorithm in \Cref{alg:ca: refining FISTA} for a choice of refining subspaces $\spcf0^n\subset\spcf0^{n+1}\subset \spcf0\cap\F H$ for $n=0,1,\ldots$. The only difference is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. Indeed, if $\spcf0^n=\spcf0=\F H$ then this is just the standard FISTA algorithm.

@@

Finally we introduce the concept of an orthogonal projection in the setting of this work. For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\Pi_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that 
$$\IP{\Pi_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$$
This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$. Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\Pi_n$ is an extension of the classical orthogonal projection. It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is well-defined. Beyond this, the Hahn-Banach theorem may allow the domain of $\Pi_n$ to be extended further, but the definition is no longer unique. For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers. To account for this possibility, we shall state that the domain of $\Pi_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.

Constant factors will generally not be tracked during the proofs in this chapter. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will frequently use the notation:
\begin{align*}
	a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
	\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
\end{align*}

\begin{algorithm}[b!]\caption{Refining sub-space FISTA}\label{alg:ca: refining FISTA}
	\centering
	\begin{algorithmic}[1]
		\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(\vart1_n)$
		\State $\varf1_0\gets \varf0_0, n\gets0$
		\Repeat
		\State $\bar{\varf0}_n \gets (1-\tfrac{1}{\vart1_n})\varf0_n + \tfrac{1}{\vart1_n}\varf1_n$
		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$
		\State $\varf1_{n+1} \gets (1-\vart1_n)\varf0_n + \vart1_n\varf0_{n+1}$
		\State $n\gets n+1$
		\Until{converged}
	\end{algorithmic}
\end{algorithm}

\section{General proof recipe}\label{sec:ca: recipe}
In this work we focus on the FISTA algorithm, however, the key ingredients of the proof do not rely on the particular structure of FISTA. In this section we will sketch the general `recipe' of the convergence proof for adaptive schemes in a Banach space setting.

During this section, we will refer to the structure of FISTA as motivation. In particular, we recall the classical FISTA convergence guarantee given in \cite[Theorem 2]{Chambolle2015}:
\begin{equation}\label{eq:ca: classical FISTA}
	t_N^2\Func0_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
\end{equation}
for some $t_N\simeq N$ and $\rho_n\geq0$.

\subsubsection{Step 1: Quantifying the scaling properties}
\begin{adaptiveStep}\label{step:ca: step 1 smoothness}
	The first step is to quantify how $\Func0$ and $\norm\cdot$ behave as the discretisation refines, or resolution increases. In \Cref{alg:ca: refining FISTA} we are given the subspaces $\spcf0^n$ which we partition into a sequence of milestones. In particular, we assume there exists $n_k\in\F N$ and constants $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that:
	$$n_0<n_1<\ldots, \qquad \norm{\argmin_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0)} \lesssim \vars3_{\Varf0}^k, \qquad \text{and}\qquad \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \lesssim \vars3_{\Func0}^{-k}.$$

	The idea is that $\spcf0^{n_k}$ is a discretisation at resolution $\meshsize^k$ for some $\meshsize<1$ and therefore the minimum of $\Func0_0$ decays exponentially while the norm of discrete minimisers potentially grows exponentially. In \Cref{sec:ca: general examples} we will see that this exponential scaling is very natural.

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm,bm}
\usepackage[round,colon,authoryear]{natbib}
\usepackage[cm]{fullpage}
\definecolor{linkColor}{rgb}{0.5, 0.5, 0.5}
\usepackage[colorlinks, allcolors=linkColor, bookmarks=True]{hyperref}
\usepackage[capitalise]{cleveref}
\usetikzlibrary{positioning,trees}
\usepackage{algorithm,algpseudocode}
\graphicspath{{Figures/}}
\DeclareGraphicsExtensions{.pdf,.png}
\numberwithin{equation}{section}
\newtheorem{definition}{Definition}[section]\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\makeatletter\let\c@definition\c@theorem\let\c@definition\c@theorem\makeatother
\makeatletter\let\c@lemma\c@theorem\let\c@lemma\c@theorem\makeatother
\makeatletter\let\c@example\c@theorem\let\c@example\c@theorem\makeatother
\makeatletter\let\c@remark\c@theorem\let\c@remark\c@theorem\makeatother
\newtheorem*{theorem*}{Theorem}

\newcommand{\Partial}[2]{\frac{\partial #1}{\partial #2}}
\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\C{A}}
\newcommand{\Vector}[3]{ \begin{pmatrix} #1 \\ #2 \\ #3 \end{pmatrix}}
\newcommand{\MTwo}[4]{\begin{pmatrix} #1 & #2 \\ #3 & #4 \end{pmatrix}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}\newcommand{\overtext}[2]{\stackrel{\text{#1}}{#2}}
\newcommand{\xmapsfrom}[1]{\reflectbox{$\xmapsto{\reflectbox{\scalebox{0.87}[0.69]{$#1$}}}$}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\renewcommand{\P}{\F{P}}\newcommand{\E}{\F{E}}\newcommand{\1}{\F{1}}
\renewcommand{\circle}[1]{\raisebox{.5pt}{\rm{\textcircled{\raisebox{-.9pt} {#1}}}}}
\newcommand{\intbar}{-\hspace{-10.5pt}\int}\newcommand{\todo}[1]{{\color{red}#1}}
\DeclareMathOperator{\st}{\;s.t.\;}\DeclareMathOperator{\as}{\;a.s.\;}\renewcommand{\epsilon}{\varepsilon}
\DeclareMathOperator*{\Union}{\bigcup}\DeclareMathOperator{\union}{\cup}
\DeclareMathOperator*{\Intersect}{\bigcap}\DeclareMathOperator{\intersect}{\cap}
\renewcommand{\bar}{\overline}\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\renewcommand{\vec}{\mathbf}
\DeclareMathOperator*{\argmin}{argmin}\DeclareMathOperator{\TV}{TV}
\DeclareMathOperator{\prox}{prox}\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}\DeclareMathOperator{\sign}{sign}

\newcounter{adaptStepCounter}
\newenvironment{adaptiveStep}{\refstepcounter{adaptStepCounter}}{}
\crefname{adaptStepCounter}{Step}{Steps}

@@

\author{Robert Tovey and Antonin Chambolle}
\date{\longdate\today}
\title{FISTA with adaptive discretisations}
\begin{document}
	\maketitle

%In many variational approaches to inverse problems, optimisation problems are often written in a continuous setting but solved with a discrete optimisation algorithm. Consider what happens when $\sqrt{e^2}$ is computed in your favourite programming language. We have asked a `continuous' question and have been given a `discrete' answer with very well controlled error bounds.
%
%The parallel to this for optimisation is that we still do not have infinite computing memory or processing power, but we still want to compute minimisers to a known accuracy with efficient implementations. It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \citep{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \citep{Mallat1999,Candes2004,Guo2007}. These are typically quite weak guarantees valid for asymptotic resolution/time and are hard to quantify in a specific example. In this work we propose an algorithm with three aims:
%\begin{itemize}
%	\item All computations are discrete but the asymptotic reconstruction is exact, even for infinite dimensional reconstructions in a Banach space, with a guaranteed rate.
%	\item Distance to the infinite dimensional minimiser can be quantified.
%	\item Discretisation is adaptively optimised for the particular minimiser.
%\end{itemize}
%
%We choose to modify the FISTA algorithm because it is quite general and performs very well in discrete optimisation problems. The strategy will be to follow the standard FISTA algorithm as closely as possible. The only difference is that at each iteration, computations will only be performed on a finite dimensional subspace. 
%
%One key issue is that FISTA is intrinsically designed to converge only in $L^2$. In finite dimensions there is no issue, all norms are equal and so convergence rates are equal for all problems up to scaling constants. On the other hand, in infinite dimensions there exist minimisers which are not in $L^2$. In this case, we find that the rate will always be slower than for standard FISTA but still at a guaranteed rate.
%
%We perform two numerical experiments where the minimiser is in $L^1\setminus L^2$ which demonstrates the reduced rate. We also show an example where the minimiser is in $\ell^2(\R^m)$ for some $m$ which is not known a priori and observe that the refining FISTA algorithm achieves linear convergence.

\section{Introduction}
The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was first proposed by \citet{Beck2009} and is now a very popular algorithm for minimising the sum of two convex functions. We will write this as the problem of computing 
\begin{equation}\label{eq: min F = fD+fC}
	u^* \in \argmin_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
\end{equation}
where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function. The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting. Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA in specific scenarios \citep{some references}.

The contribution of this work is a modified FISTA algorithm which achieves two key properties:
\begin{itemize}
	\item we extend the convergence results to the case $\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
	\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation in both measures of time and computer memory requirements.
\end{itemize}
\todo{There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for the use outside of Hilbert spaces is the key novelty.} Some other works for FISTA-like algorithms include \citep{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in \Cref{thm: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations.

\subsection{Canonical example}
While the analysis of this work is applicable to general choices of $\func1$ and $\func2$, we will refer back to the example of the (Beurling) Lasso model both for motivation and for numerical examples. We state the Lasso energy as
\begin{equation}\label{eq: Lasso energy intro}
	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1,
\end{equation}
where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\Domain)\to \R^m$ is the forward map and $\mu>0$ is an appropriately chosen scalar. We have $\F H = L^2(\Domain)$ and $\spcf0 = \C M(\Domain)$ the space of measures on $\Domain$ equipped with the $L^1$ norm. In the continuous setting $\Domain = [0,1]^d$ and for discrete we have $\Domain=\F N$, i.e. $\spcf0\cong\ell^1(\R)$.

It is a well-known result of representer theorems for $\Func0$ \citep{Unser2016,Boyer2019} that there exist minimisers of the form 
\begin{equation}
	\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, 
\end{equation}
for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$.

This is a practical example where we have the relation $\varf0^*$ does not lie in the Hilbert space $\F H$, and yet it is very easy to approximate with a discrete basis. Our approach will be to use finite elements which can clearly generalise to other examples.

\subsection{Outline}
This chapter is organised as follows. \Cref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of \Cref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec: recipe}, then we state the specific results in the case of FISTA in \Cref{sec: FISTA convergence}. The main results are \Cref{thm: exponential FISTA convergence} and \Cref{thm: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

\Cref{sec: general examples} presents some general results for the application of \Cref{alg: refining FISTA} and \Cref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate $\varf0^*$, estimate the convergence of $\Func0$, and identify the support of $\varf0^*$. The numerical results in \Cref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.

\section{Definitions and notation}\label{sec: prelims}
We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
\begin{equation} 
	\exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).
\end{equation}
Furthermore, define the translated energy
\begin{equation}
	\Func0_0\colon\spcf0\cup\F H\to \R,\qquad \Func0_0(\varf0) \coloneqq \Func0(\varf0)-\Func0(\varf0^*).
\end{equation}
Note that the value of $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be. \todo{We could just say $E_0=E$ without loss of generality, just like $L=1$.}

The proposed generalised FISTA algorithm is stated in \Cref{alg: refining FISTA} for an arbitrary choice of refining subspaces $\spcf0^n\subset \spcf0\cap\F H$ for $n=0,1,\ldots$. The only difference is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. If $\spcf0^n=\spcf0=\F H$ then we recover the standard FISTA algorithm.

@@

One defining property of the FISTA algorithm is an appropriate choice of inertia, dictated by $\vart1_n$. In particular, we will say that $(\vart1_n)_{n=0}^\infty$ is a \emph{FISTA stepsize} if
\begin{equation}\label{def: t_n and rho_n}
	t_0 = 1, \qquad t_n \geq 1, \qquad \text{and}\qquad \rho_n \coloneqq t_n^2 - t_{n+1}^2 + t_{n+1} \geq 0\qquad \text{ for all }n=0,1,\ldots
\end{equation}

Finally we introduce the concept of an orthogonal projection in the setting of this work. For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\Pi_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that 
$$\IP{\Pi_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$$
This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$. Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\Pi_n$ is an extension of the classical orthogonal projection. It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is sufficiently well-defined. Beyond this, the Hahn-Banach theorem may allow the domain of $\Pi_n$ to be extended further, but the definition is no longer unique. For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers. To account for this possibility, we shall state that the domain of $\Pi_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.

The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
\begin{align*}
	a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
	\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
\end{align*}

\begin{algorithm}\caption{Refining sub-space FISTA}\label{alg: refining FISTA}
	\centering
	\begin{algorithmic}[1]
		\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(\vart1_n)$
		\State $\varf1_0\gets \varf0_0, n\gets0$
		\Repeat
		\State $\bar{\varf0}_n \gets (1-\tfrac{1}{\vart1_n})\varf0_n + \tfrac{1}{\vart1_n}\varf1_n$
		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
		\State $\varf1_{n+1} \gets (1-\vart1_n)\varf0_n + \vart1_n\varf0_{n+1}$
		\State $n\gets n+1$
		\Until{converged}
	\end{algorithmic}
\end{algorithm}

\section{General proof recipe}\label{sec: recipe}
In this section we give an intuitive outline of the full proof for convergence of \cref{alg: refining FISTA} before giving formal theorems and proofs in the next section. First we recall the classical FISTA convergence guarantee given by \citet[Theorem 2]{Chambolle2015}:
\begin{equation}\label{eq: classical FISTA}
	t_N^2\Func0_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
\end{equation}
for some FISTA stepsize choice $t_N\simeq N$ and $\rho_n\geq0$.

\paragraph{Step 1: Quantifying the stability}
\begin{adaptiveStep}\label{step: step 1 stability}
	The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$. In the notation of \cref{alg: refining FISTA}, \cref{thm: mini FISTA convergence} shows that 
	\begin{equation}\label{eq: mini FISTA convergence}
		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
	\end{equation}
	for $\varf2_n = \argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$. The similarities to \eqref{eq: classical FISTA} are clear. If $\spcf0^n=\spcf0$, then we have $\varf2_n=\varf0^*$ and the two estimates agree. These extra terms quantify the robustness to changing of discretisation.
\end{adaptiveStep}
